Object-based Auditory Scenes Similarity Retrieval and Classification With Wavelet Scattering

### 2016-07-12 paper/structureScene.tex
address ja comments in VI

At the end, each scene $s_u$ is described by a set of clusters $C_u$. One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, which clusters not over a single scene, but over the whole dataset, and re-projects each scene in the resulting enhanced feature space. \ja{This sentence is also a big unclear.}

>>>>

At the end, each scene $s_u$ is described by a set of clusters $C_u$. One should note that this quantization approach differs from unsupervised learning schemes such as the ones studied in \cite{bisot2016acoustic}, where the scene features are projected in a dictionary learned from the entire dataset.

%which clusters not over a single scene, but over the whole dataset, and re-projects each scene in the resulting enhanced feature space. \ja{This sentence is also a big unclear.}
